---
title: "reproducible pitch"
author: "Audrey Clausell"
date: "2023-08-27"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## developping data product final project  


Welcome to my presentation about my Shiny app!


## overview

Here's a brief overview of what my app does.

Based on the IRIS data available in the ggplot2 package, my app calculate the mean of one variable (sepal.length, sepal.width,petal.length, petal.width) and one specie. 

The user select both the variable and the sepcie with 2 different boxes where varaibles are written. 

## Data IRIS 

Let's take a look at some data from the app using R code:

```{r}
head(iris)
```

For example, sepal.length has a 5.006 mean for setosa

```{r}
subset_data <- subset(iris, Species == "setosa")
mean(subset_data$Sepal.Length)
```

## explaination of the code : server 

In server, the app calls packages : 


```{r}
library(shiny)
library(ggplot2)
```

I add "if (!is.null(selected_var) && !is.null(selected_species))" to not bug the app. The user can't click "calculate" when boxes are empty. 

## explaination of the code : ui

2 select inputs : 

1. "selectInput("variable", "Select a Variable:", choices = colnames(iris[1:length(iris)-1]))" for the variable, removing the last column (specie) to select only numeric 

2. "selectInput("species", "Select a Species:", choices = unique(iris$Species))"

One action button : "actionButton("calculate", "Calculate Mean")"

## Link to my app and github 

app : https://audreyclausell.shinyapps.io/project/

github repo : https://github.com/snoopyaudrey/developping_data_product








